---
title: "Tasting Chocolate"
author: "John Letteboer"
date: "11/29/2015"
output: 
  html_document: 
    fig_caption: yes
    keep_md: yes
    theme: cosmo
---
```{r set-options, echo=FALSE, cache=FALSE}
options(width = 180)
```

Q1: Is there a difference taste score between female and male.

- H~0~: man = female
- H~1~: man $\ne$ female
- Confidence interval is .95
- $\alpha$ = .05

Loading required packages.
```{r message=FALSE}
library(ggplot2)
library(RColorBrewer)
library(psych)
```

Load the dataset.
```{r}
df <- read.csv("Tasting_chocolate.csv", header=TRUE, sep = ";")
```

After loading the dataset let's have a look at the data.
```{r}
dim(df)
head(df, 2)
str(df)
summary(df)
```

We can see the dataset has 150 objects and 4 variables, `type`, `gender`, `gender.1` and `taste`.

## t-Test
### First Step
#### 1. Are there missing values?
```{r}
any(is.na(df))
```

As we can see there are no missiong values.

#### 2. Are there outliers?
Let's make a boxplot to see if there are any outliers.

```{r}
boxplot(df$taste ~ df$gender, col="gray", outcol="red")
```

There are no outliers.

#### 3. Are the data normal distrubuted
Let make some histograms
```{r}
cols <- brewer.pal(11,"Set1")
ggplot(df, aes(taste, fill=gender)) + 
    facet_grid( type ~ gender) + 
    geom_histogram(binwidth=.5, alpha=.5, position="identity") + 
    theme_bw() + 
    scale_fill_manual(values = cols) + 
    theme(legend.position="none")
```

From the histograms we can see that the data is looks normal distrubuted.

Now calculate this with the Kurtosis and Skewness.

- The skewness is a measure of symmetry. As a rule, negative skewness indicates that the mean of the data values is less than the median, and the data distribution is left-skewed. Positive skewness would indicates that the mean of the data values is larger than the median, and the data distribution is right-skewed.
- The kurtosis is a measure of the peakedness of the data distribution. Negative kurtosis would indicates a flat data distribution, which is said to be platykurtic. Positive kurtosis would indicates a peaked distribution, which is said to be leptokurtic. Incidentally, the normal distribution has zero kurtosis, and is said to be mesokurtic.

```{r}
kurtosis <- aggregate(taste ~ gender + type, df, kurtosi)
skewness <- aggregate(taste ~ gender + type, df, skew)
kurtosis
skewness
```

### Second step
Determine equality of variances by doing a F-test.
```{r}
var.test(df$taste[df$gender=="female"], df$taste[df$gender=="male"])
```

The p-value > $\alpha$ (.05), we accept H~0~

### Third step
Let's do a independent 2-group t-test of `taste` over `gender`
```{r}
t.test(taste ~ gender, df)
```

## ANOVA
First resize lenght of `type`, because it's better for plotting.
```{r}
df$type_short[df$type == "Own brand Carrefour"] <- "own"
df$type_short[df$type == "Chocolate bar Van Houten"] <- "bar"
df$type_short[df$type == "Chocolate milk Van Houten"] <- "milk"
df$type_short <- as.factor(df$type_short)
```

Create a boxplot to see if there are outliers per type
```{r}
boxplot(df$taste ~ df$type_short, col="gray", outcol="red")
```

Create histograms to see if the data is normal distrubuted
```{r}
ggplot(df, aes(taste, fill=type)) + 
    facet_grid(type~.) + 
    geom_histogram(binwidth=.5, alpha=.5, position="identity") + 
    theme_bw() + 
    scale_fill_manual(values = cols) + 
    theme(legend.position="none")
```

There are some outliers but not that bad.

Create ANOVA
```{r}
aov1 <- aov(taste ~ type_short, df)
summary(aov1)
TukeyHSD(aov1)
plot(TukeyHSD(aov1))

aov2 <- aov(taste ~ gender, df)
summary(aov2)
TukeyHSD(aov2)
plot(TukeyHSD(aov2))

par(mar = c(5,12,4,2), cex = 0.7)
aov3 <- aov(taste ~ gender * type_short, df)
summary(aov3)
TukeyHSD(aov3)
plot(TukeyHSD(aov3), las = 2)
```
