---
title: "Tasting Chocolate"
author: "John Letteboer"
date: "11/23/2015"
output: 
  html_document: 
    fig_caption: yes
    fig_height: 6
    fig_width: 10
    keep_md: yes
    theme: cosmo
---
```{r set-options, echo=FALSE, cache=FALSE}
options(width = 180)
```

Q1: Is there a difference taste score between female and male.

- H0: man = female
- H1: man $\ne$ female

Loading required packages.
```{r}
library(ggplot2)
library(RColorBrewer)
library(psych, quietly = T)
#library(MVN)
```

Load the dataset.
```{r}
df <- read.csv("Tasting_chocolate.csv", header=TRUE, sep = ";")
```

After loading the dataset let's have a look at the data.
```{r}
dim(df)
head(df)
str(df)
summary(df)
#describeBy(df, group = "gender")
```

We can see the dataset has 150 objects and 4 variables, `type`, `gender`, `gender.1` and `taste`.

### First Step
#### 1. Are there missing values?

```{r}
any(is.na(df))
```

As we can see there are no missiong values.

#### 2. Are there outliers?
Let's make a boxplot to see if there are any outliers

```{r}
boxplot(df$taste ~ df$gender)
points(df$taste~df$gender,col="red")
```

There are no outliers.

#### 3. Are the data normal distrubuted

Let make some histograms
```{r}
cols <- rev(brewer.pal(7,"Spectral"))
ggplot(df, aes(taste, fill=gender)) + 
    facet_grid( type ~ gender) + 
    geom_histogram(binwidth=.5, alpha=.5, position="identity") + 
    theme_bw() + 
    scale_fill_manual(values = cols)
```

Let make two subsets of gender, `male` and `female`.
```{r}
male <- df[df$gender == "male",]
female <- df[df$gender == "female",]
```

Let see if the data is normal distributed.
```{r}
par(mfrow = c(1, 2))
hist(male$taste, 
     labels = TRUE, 
     breaks = c(-4:4), 
     main="Histogram Male", 
     xlab="Taste", 
     col="lightblue", 
     ylim = c(0,30))
hist(female$taste, 
     labels = TRUE, 
     breaks = c(-4:4), 
     main="Histogram Female", 
     xlab="Taste",
     col="lightblue", 
     ylim = c(0,30))
```

As we can see is the data normal distrubuted.

Let do a independent 2-group t-test
```{r}
t.test(taste ~ gender, df)
```




```{r}
df$type_short[df$type == "Own brand Carrefour"] <- "own"
df$type_short[df$type == "Chocolate bar Van Houten"] <- "bar"
df$type_short[df$type == "Chocolate milk Van Houten"] <- "milk"
df$type_short <- as.factor(df$type_short)

boxplot(df$taste ~ df$type_short)
boxplot(df$taste ~ df$gender)

aov1 <- aov(df$taste ~ df$type_short)
summary(aov1)
TukeyHSD(aov1)
plot(TukeyHSD(aov1))

aov2 <- aov(df$taste ~ df$gender)
summary(aov2)
TukeyHSD(aov2)
plot(TukeyHSD(aov2))

aov3 <- aov(df$taste ~ df$gender * df$type_short)
summary(aov3)
TukeyHSD(aov3)
plot(TukeyHSD(aov3), las = 2)
```
